\section{\xlabel{engineering}Engineering Data\label{se:eng}}

Recipes also exist for processing engineering data, usually taken with
the shutter closed and the telescope stationary. Historically, the
real-time sequencer (RTS) was not involved in such measurements which
prevented the pipeline from processing these data due to missing FITS
headers and other essential metadata.

In September 2010 is was decided that the pipeline be used to process
and analyze data taken in engineering mode, and a simulated RTS is
used to generate metadata. Support for engineering data is currently
quite rudimentary with only a single recipe available.

Note that in order to process data taken in engineering mode, the
\verb+-eng+ option must be given to the \oracdr\ initialization
script.

\subsection{NEP}

Measurements of the noise-equivalent power (NEP) are processed with
the \task{ENG\_NEP} recipe. The `observation' consists of a series of
NOISE measurements at different pixel heater and detector bias
values. The recipe is designed to run offline, after the observation
has finished.

The NEP is calculated for each subarray at each setting. These
per-bolometer NEP images are combined to form a 4-d hypercube with
axes bolometer row, bolometer column, heater setting and bias setting
for each subarray. These hypercubes are named
\verb+sXXYYYYMMDD_MMMMM_nep.sdf+ where \verb+sXX+ is the subarray
label (e.g.\ \verb+s8a+).

From these data, the effective and RMS NEP is calculated at each
heater and bias setting, stored as a 2-d image with the heater and
bias values as the X- and Y axes. These images have suffices of
\verb+_effnep+ and \verb+_rmsnep+ respectively.

A number of log files are also written. The first is called
\verb+log.bolonoise+ which contains the noise properties for each
heater and bias setting and all subarrays. Log files for the `mapping
speed' parameter for each subarray are written separately with the
name \verb+log.mapspeed_SXX+ where \verb+SXX+ is the subarray
(e.g.\ s4a). The mapping speed is given by $N_{\rm bol} / {\rm
  NEP}_{\rm RMS}^2$ and is calculated for the best $N_{\rm bol}$
bolometers between 300 and 1000 in steps of 100 bolometers.

The recipe does not display any data.
