\section{\xlabel{overview}Overview of the SCUBA-2 pipeline\label{se:overview}}

\subsection{Quicklook (QL) pipeline}

The QL pipeline uses a task called \verb+qlgather+ to monitor the
DRAMA processes and write out a flag file with the names of the files
to process. The pipeline reads that flag file and processes each of
the named files. \verb+qlgather+ collates data with the same subscan
number. If new data are detected before all the expected files for
the current subscan are in place, the new data take precedence and
processing of the current subscan may be skipped.

Fastramp flatfields taken as part of each observation are processed
and stored in the calibration system. The responsivity image for all
four subarrays (along with the previous and percentage-change images)
are displayed in a Kapview window.

Pointing and focus data are processed using the iterative map maker
with a configuration file optimized for such observations of bright
compact sources. Corresponding fastramp flatfields are obtained from
the calibration system. For pointing observations an FCF is derived if
the source is a known calibrator. The image is displayed using \GAIA,
showing in window 1, and then combined with the current coadd image
(if one exists). The coadd image is displayed in another \GAIA\ window
(2), and its error component (noise) in another (3). For focus
observations, the data for each SMU position is processed separately
and combined into a three-dimensional data cube. The name of the
pointing coadd or focus cube is written to a flag file
(\verb+.sYYYYMMDD_MMMMM.ok+, where \verb+MMMMM+ is the current
observation number) for further analysis by the telescope
POINTING\_FOCUS task. The pipeline makes its own estimates of the
pointing and focus solution, which are written to log files. Any
temporary files created during this processing are deleted, keeping
only files with a suffix \verb+_reduced+ or \verb+_foc+ for pointing
and focus respectively.

Science data are processed as noise observations. The noise between 2
and 10 Hz is calculated along with the noise equivalent power (NEP)
and the weighted NEP. These values undergo quality assurance checks to
ascertain whether or not the instrument is still operating within
specified limits. The focal-plane noise distribution is displayed in a
Kapview window.

Data from other observing modes are processed as per their own recipes.

\subsection{Summit pipeline}

The summit pipeline is the main image-making pipeline running at the
telescope. It will use all available data for processing (unlike the
QL which will skip data to deal with the latest files), and as such
may fall behind for several subscans. However, the processing is
structured such that the processing for a given observation should be
complete before a new observation begins.

Pointing and focus observations (along with setups, noise and skydips)
are processed in a similar manner to the QL, though no data are
skipped.

The pipeline checks for the presence of flag files which are updated
with the names of new data as they are written to disk. As each file
is picked up by the pipeline, it checks to see how much time has
elapsed since the last map was made. If the time exceeds a threshold
(typically about one-and-a-half to two minutes), then a new map is
made using all of the data taken since the previous map. The map is
calibrated in mJy\,beam$^{-1}$ using the standard FCF. If it is too
soon to make a new map, the raw data are flatfielded and left on disk
(suffix \verb+_ff+). These files will be deleted once a new image is
made.

The new image is combined with the existing coadd (if appropriate) and
a new NEFD image is calculated. Note that the summit pipeline coadds
images for a given source across multiple observations so fainter
features will be revealed as the integration time increases. If a new
image was not created during the latest pass through the recipe then
all flatfielded data files needed to create a map are left on disk.

\subsection{Science pipeline}

The science pipeline examines all the data files given to it and works
out which files are related and should be processed together
(``batch'' mode). Each observation is still processed separately to
produce an image, which is calibrated in mJy\,beam$^{-1}$ (unless
otherwise specified by the recipe). All the images for a given source
are combined into a single coadd using inverse-variance weighting. If
the source is a known calibrator then the images are checked for
offsets and, if necessary, shifted to place the source at the correct
position.

At the end of processing, all temporary files are deleted: the only
data files left on disk will have the suffix \verb+_reduced+.

Recipes exist for a number of different target types which contain
different processing steps, relevant to each particular target
type. These are bright or faint compact (such as planets, T-Tauri
stars or extragalactic blank fields respectively) and extended (such
as Galactic star-forming regions). Examples of these steps include
applying a matched-filter to enhance point-source detectability or
running a clump-finding algorithm.

Note that additional recipes exist for determining the noise
properties of the science data. The first performs the same noise
analysis and QA checks as the QL pipeline. This can be run offline by
adding the recipe name ASSESS\_DATA\_NOISE to the \oracdr\ command
line. The second recipe calculates the noise and NEP properties in
addition to carrying out the standard map-making procedure, and
compares the noise properties with that expected from the SCUBA-2
integration time calculator. This recipe is called
REDUCE\_SCAN\_CHECKRMS. See the documentation below for further
details.
